Effect of temporal sampling

### 2019-10-31 R/temporal-sampling.Rmd
work on 10/31

**Note for next time: write function to compute the tolerance to error against sample size**

@@

for (i in shift_vector) {
  # Set simulation parameters
mu = 0
sigma = 0.1
phi = 1
shift_time = i
max_time = 100

@@

temporary <- ut(y=exp(ar1), sample_size = c(10:50), threshold_error = c(1:10), each = 1, type="mean")

@@

# Something is wrong here, it is sometimes adding >900 samples.I think it has to do with the while loop in the ut() function.
ggplot(out_convergence_cptmean, aes(sample_size,number_sample_added)) + geom_point(alpha=.3) + ylim(0,25)

>>>>

@@

for (i in shift_vector) {
  # Set simulation parameters
  mu = 0
  sigma = 0.5
  phi = 1
  shift_time = i
  max_time = 100

@@

  temporary <- ut(y=exp(ar1), sample_size = c(10:50), threshold_error = c(1:4), each = 1, type="mean")

@@

# Something is wrong here, it is sometimes adding >900 samples.I think it has to do with the while loop in the ut() function.
ggplot(out_convergence_cptmean, aes(sample_size,number_sample_added)) + geom_point(alpha=.15)  + facet_wrap(~threshold_error)
